---
title: "BentoBoxData"
author: "Nicole Kramer"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Introduction to BentoBox}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sample experimental data

This package provides subsets of publicly available Hi-C, ChIP-seq, 
DNA looping, GWAS, and COVID-19 datasets. The genomic datasets are all
in reference to the `hg19` genome build. These datasets are included in
the `data` directory and can be loaded with the `data()` call:

```{r}
library(BentoBoxData)
data("IMR90_HiC_10kb")
```

The full versions of these datasets can be found at the citations provided
in each data documentation file (e.g. `?bb_imrHicData`).

The `BentoBox` vignettes detail how to visualize these datasets.

# Sample raw files

Small, example `.bigwig` and `.hic` files are included in the `inst/extdata` 
directory to demonstrate the functionality of the `BentoBox` functions
`bb_readBigwig` and `bb_readHic`:

```{r}
bwFile <- system.file("extdata/test.bw", package = "BentoBoxData")
hicFile <- system.file("extdata/test_chr22.hic", package = "BentoBoxData")
```

# CytoBand datasets

Giemsa stain band information was compiled from the UCSC Genome Browser for the 
following genome assemblies:
* `dm6`
* `danRer10`
* `hg18`
* `hg19`
* `hg38`
* `mm9`
* `mm10`
* `rn5`
* `rn6`

Please refer to the USCS Genome Browser database for more information on these
data: 

> Navarro Gonzalez J, Zweig AS, Speir ML, Schmelter D, Rosenbloom KR, Raney BJ,
> Powell CC, Nassar LR, Maulding ND, Lee CM, Lee BT, Hinrichs AS, Fyfe AC, 
> Fernandes JD, Diekhans M, Clawson H, Casper J, Benet-Pagès A, Barber GP, 
> Haussler D, Kuhn RM, Haeussler M, Kent WJ. The UCSC Genome Browser database:
> 2021 update. Nucleic Acids Res. 2021 Jan 8;49(D1):D1046-D1057. 
> doi: 10.1093/nar/gkaa1070. PMID: 33221922; PMCID: PMC7779060.

These data are used in the `BentoBox` `bb_plotIdeogram` function and can be 
loaded with `data()`.

# Session info

```{r}
sessionInfo()
```