---
title: "plotgardenerData"
author: "Nicole Kramer"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{plotgardenerData}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sample experimental data

This package provides subsets of publicly available Hi-C, ChIP-seq, 
DNA looping, GWAS, and COVID-19 datasets. The genomic datasets are all
in reference to the `hg19` genome build. These datasets are included in
the `data` directory and can be loaded with the `data()` call:

```{r}
library(plotgardenerData)
data("IMR90_HiC_10kb")
```

The full versions of these datasets can be found at the citations provided
in each data documentation file (e.g. `?IMR90_HiC_10kb`).

The `plotgardener` vignettes detail how to visualize these datasets.

# Sample raw files

Small, example `.bigwig` and `.hic` files are included in the `inst/extdata` 
directory to demonstrate the functionality of the `plotgardener` functions
`readBigwig` and `readHic`:

```{r}
bwFile <- system.file("extdata/test.bw", package = "plotgardenerData")
hicFile <- system.file("extdata/test_chr22.hic", package = "plotgardenerData")
```

# Session info

```{r}
sessionInfo()
```